Turbo fast no compromise gravitational wave parameter estimation

### 2023-01-08 src/tex/ms.tex
Add ppPlot script
Add PP plots description

To demonstrate the robustness of our pipeline, we use it to recover the
parameters of a set of simulated signals. We create a set of simulated signals
and inject them into simulated noise, generated under the Gaussian noise
assumption using the designed PSD for every detector. Then we run our pipeline
given the simulated data and determine the credible interval at the true
parameters of the injected signals. Given the set of credible values, we can
check whether the true value lies within a certain credible interval at a
reasonable frequency. If our pipeline is perfect, we should find the true
parameters lie within $x\%$ credible interval $x\%$ of the time, e.g. the true
value should lie within the $50\%$ credible interval $50\%$ of the time.
Deviation from this behavior suggests the pipeline is either over-confident or
too conservative.

% State the distribution of injected population
We sample 1000 events from the following distribution of parameters:

% Show injection pp plot
The result of the injection studies is shown in \ref{fig: ppplot}.

\begin{figure}
    \includegraphics[width=0.99\linewidth]{static/ppplot.png}
    \caption{ \kw{I am pretty sure I am doing something wrong about the ppplot.
        Given injected q=1, there is no way the quantile is not 1, which is what
        bias the result seemingly.} }
    \label{fig:ppplot}
    \end{figure}

>>>>

To demonstrate the robustness of our pipeline, we use it to recover the
parameters of a set of simulated signals. We create a set of simulated signals
and inject them into simulated noise, generated under the Gaussian noise
assumption using the designed PSD for every detector. Then we run our pipeline
given the simulated data and determine the credible interval at the true
parameters of the injected signals. Given the set of credible values, we can
check whether the true value lies within a certain credible interval at a
reasonable frequency. If our pipeline is perfect, we should find the true
parameters lie within $x\%$ credible interval $x\%$ of the time, e.g. the true
value should lie within the $50\%$ credible interval $50\%$ of the time. In
other word, the percentiles of the true parameters should be uniformly
distributed. Deviation from this behavior suggests the pipeline is either
over-confident or too conservative.

% State the distribution of injected population
We sample 1000 events from the following distribution of parameters detailed in
table \ref{tab:parameters}.
The same distribution of parameters are used as the prior in the PE process.
The simulated signals have a 16 seconds segment length,
and we project the signal on the LIGO Hanford, Livingston and Virgo detector.
We used the designed sensitivity curve for each detector to generate the noise \kw{cite}.
We use a minimum frequency cutoff of 30 Hz with a sampling rate of 2048 Hz.

\begin{table*}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l }
    \hline
    \hline
    Parameters &  Description & Prior range\\

    $M_c$ & chirp mass & $[10, 50] M_\odot$\\
    $q$ & mass ratio & $[0.5, 1]$\\
    $\chi_1$ & dimensionless spin of the primary mass & $[-0.5, 0.5]$\\
    $\chi_2$ & dimensionless spin of the secondary mass & $[-0.5, 0.5]$\\
    $d_L$ & luminosity distance & $[300, 2000] Mpc$\\
    $t_c$ & coalescence time & $[-0.5, 0.5] s$\\
    $\phi_c$ & coalescence phase & $[0, 2\pi]$\\
    $\cos{\iota}$ & cosine of inclination angle & $[-1, 1]$\\
    $\psi$ & polarization angle & $[0, \pi]$\\
    $\alpha$ & right ascension & $[0, 2\pi]$\\
    $\sin{\delta}$ & sine of declination & $[-1, 1]$\\

    \hline
    \hline
    \end{tabular}
    \caption{Parameters used in the injection-recovery test.}
    \label{tab:parameters}
    \end{center}
\end{table*}

% Show injection pp plot
The result of this injection-recovery campaign is shown in fig. \ref{fig: ppplot}. We
computed the quantile of which the true value lies for each marginalized
distribution, then plotted the cumulative distribution of these quantiles. The
shadow band denotes the 95\% credible interval drawn from a uniform distribution
with the same number of events. We can see most the injection-recovery result
lies within the band drawn from a uniform distribution, showing our inference
results agree well with a uniform distribution. There is a small deviation from
a uniform distribution for the secondary spin $\chi_2$, which is not too
alarming since we are computing the quantile for 11 parameters. Having one of
them lying briefly outside the 95\% band does not mean the inference is bias.

To quantify how well our result agrees with a uniform distribution, we can
compute the Kolmogorov-Smirnov test p-values for each marginalized distribution.
If the p-value is too low, often chosen to be $0.05$, then it means our result
does not agree with a uniform distribution, hence it could be biased. The
p-values for each marginalized distribution are shown in the legend of fig.
\ref{fig: ppplot}. We can see most of them are well above the $0.05$ threshold,
except for $\chi_2$, which is mildly below the threshold. Once again, assuming
these p-values are drawn from a uniform distribution, given $11$ draws (the
number of parameters in our inference), it is not abnormal to have one of the
parameters lies slightly outside the threshold. To assess whether this is
expected, we can compute the combined p-value for these 11 parameters, which is $0.47$.
This shows our inference pipeline performs properly on simulated data.
Indeed, the accuracy of our inference pipeline is consistent with other works\kw{cite}.

\begin{figure}
    \script{ppplots.py}
    \includegraphics[width=0.99\linewidth]{figures/ppplot.pdf}
    \caption{Result of 1000 injections drawn from the 16 seconds prior.}
    \label{fig:ppplot}
    \end{figure}
